
y_as_polynomial is a function that takes in a response vector y, a covariate vector x and a significance level alpha.

The function models y as a polynomial function of x. 
To find the degree of the polynomial, the function continues to add terms until the term with the highest order, z^(p+1) is no longer significant at user provided level 
alpha. The function then returns the polynomial model with degree p.

```{r}

#defining the function, alpha = 5% is the placeholder
y_as_polynomial <- function(y, x, alpha = 0.05){
  
  #fitting the first model to y ~ x 
  model <- lm(y~x)
  
  #starting counter i at 1
  i=1

  #while loop to continuously fit models until significance level is below alpha
  while ((summary(model)[["coefficients"]][(i+1),4] < alpha)){
    
    #increase counter every loop
    i <- i+1  
  
    #update the equation and refit model to polynomial of degree i  
    model <- lm(y~ poly(x, i, raw = TRUE))
  }
  
  #return desired model of degree i-1
  lm(y~ poly(x,(i-1), raw = TRUE))
  
  
  
}
```

Here we have a simple example of implementation taken from the assignment paper

```{r}
y <- c(6.08, 6.42, 6.13, 7.94, 4.72, 8.13, 6.31, 4.62, 9.40, 3.73, 7.94, 7.52)
x <- c(3.77, 3.92, 3.79, 4.66, 3.18, 4.77, 3.87, 3.14, 6.24, 2.75, 4.66, 4.44)

y_as_polynomial(y,x, alpha = 0.05)


```
