
Bisection_Method is a function that that takes in a function and a vector with two numeric elements. These elements will be the min and max of the interval. 
The Bisection_Method function will return the point on the interval that makes the inputted function equal to 0 within an error of 1*10^(-6). 
This function assumes that the inputted function only has a single root in the interval.

```{r}

#defining the function
Bisection_Method <- function(func, interval){
  
  #setting the error to 1*10^(-6)
  target_accuracy <- (1*10**(-6))
  #getting the min and max of the interval
  x1 <- interval[1]
  x2 <- interval[2]
   
  #run this loop until we are within the desired error of the root.
  while(abs(x1-x2)>target_accuracy){
  
    #set the mid point as x prime
    x_prime <- (1/2)*(x1+x2)  
    
    #set the function at point x prime as f(x prime)
    f_x_prime <- func(x_prime)

    #check to see if the midpoint is the root, break if it is
    if (f_x_prime == 0){
      
      break
      
    #check if the sign of f(x1) is the same as f(x prime)
    }else if (sign(func(x1)) == sign(f_x_prime)){
        
        #if it is, move the max point x1 to the halfway point x prime
        x1 <- x_prime
        
    #if the sign of f(x1) is NOT the same as f(x prime) and f(x prime) does 
    #not equal 0, then move the min of the interval to x prime
    }else{
      
        x2 <- x_prime
      }
  }
  
  #return the estimated point
  (1/2)*(x1+x2)
  
}

```

Here we have a simple example of implementation taken from the assignment paper

```{r}

f <- function(x){
  # The function for which we wish to find the root
  cos(x)+exp(x)
}

Bisection_Method(f, c(-pi, pi))

```
Bisection_Method is a function that that takes in a function and a vector with two numeric elements.
These elements will be the min and max of the interval. The Bisection_Method function will return the point on the interval that makes the inputted 
function equal to 0 within an error of 1*10^(-6). This function assumes that the inputted function only has a single root in the interval.

```{r}

#defining the function
Bisection_Method <- function(func, interval){
  
  #setting the error to 1*10^(-6)
  target_accuracy <- (1*10**(-6))
  #getting the min and max of the interval
  x1 <- interval[1]
  x2 <- interval[2]
   
  #run this loop until we are within the desired error of the root.
  while(abs(x1-x2)>target_accuracy){
  
    #set the mid point as x prime
    x_prime <- (1/2)*(x1+x2)  
    
    #set the function at point x prime as f(x prime)
    f_x_prime <- func(x_prime)

    #check to see if the midpoint is the root, break if it is
    if (f_x_prime == 0){
      
      break
      
    #check if the sign of f(x1) is the same as f(x prime)
    }else if (sign(func(x1)) == sign(f_x_prime)){
        
        #if it is, move the max point x1 to the halfway point x prime
        x1 <- x_prime
        
    #if the sign of f(x1) is NOT the same as f(x prime) and f(x prime) does 
    #not equal 0, then move the min of the interval to x prime
    }else{
      
        x2 <- x_prime
      }
  }
  
  #return the estimated point
  (1/2)*(x1+x2)
  
}

```

Here we have a simple example of implementation taken from the assignment paper

```{r}

f <- function(x){
  # The function for which we wish to find the root
  cos(x)+exp(x)
}

Bisection_Method(f, c(-pi, pi))

```
