
Binomial_function is a function that takes in three parameter: n, the number of Bernoulli random variables, trials, the number of trails in each Bernoulli random 
variable, and p, the common probability shared among the Bernoulli random variables. It uses a separate function that I have also created and defined locally, 
Bernoulli, which takes in two variables: trials and p, defined the same as above. 

```{r}

# define the function
Binomial_function <- function(n,trials,p){
  
  #First, we define the function Bernoulli

  Bernoulli <- function(trials,p){
    
    #Create inputted "trials" number of uniform random variable observations 
    #using runif()
    
    unif <- runif(trials, 0, 1)
    
    #set counter j and define as placeholder 0
    j=0
    
    #loop through the created uniform observations and set to either 0 or 1
    for (i in unif){
      
      j=j+1
      
      if (i<=p){
      
        unif[j] <- 1  
      
      }else{
      
        unif[j] <- 0
        
      }
    
    }
    
    #return the uniform data morphed into Bernoulli data
    unif
  
    }
  
  #create counter i and set to placeholder value 0
  i <- 0
  
  #create result vector and set to empty placeholder
  result <-c()
  
  # loop through this code while the counter is less than inputted value n
  while (i < n){
    
    #set x to "trials" amount of observations of a Bernoulli random variable
    x<-Bernoulli(trials, p)
    
    #set counter z to placeholder 0
    z <- 0
    
    #loop through Bernoulli observations in x
    for (j in x){
      
      #check to see if trial was a success
      if (j == 1){
        
        #if it was, success counter z increases by 1
        z<-z+1
        
      }

    }
    
    #after finding how many success in Bernoulli x, append counter to result
    result <- append(result, z)
    
    #increase while loop counter by 1
    i <- i+1
  }
  
  #return binomial results 
  result

  
}
```

Here we have a simple example of implementation

```{r}

Binomial_function(10,5,0.7)

```
