
NC_from_central_and_poisson is a function that takes in three parameters: lambda, where lambda is the non-centrality parameter of the desired non-central chi-squared random variable, k, where k is the degrees of freedom of the desired non-central chi-squared random variable, and n, where n is the desired sample size from the non-central chi-squared random variable.

The function checks to see if n and k are positive integers and if lambda is non-negative. Returns an error if any are untrue.

The function will output to the user a vector of n samples from a non-central chi-squared random variable with degrees of freedom k and non-centrality parameter lambda.
 
```{r}

NC_from_central_and_poisson <- function(lambda,k,n){
  
  
if (n < 0 || k < 0) {
stop("the sample size and degrees of freedom must be > 0")
} 
  
if (k %% floor(k) != 0 || n %% floor(n) != 0) {
stop("n and k must be integers")
}    
  
if (lambda < 0) {
stop("lambda must be >= 0")
}    
    
z=rpois(n,lambda/2)
rchisq(n,k+2*z)

}

```


Here, we verify that the function does generate samples from a non-central Chi-Squared random variable by checking to see if the distribution lines up with the rchisq() function which we know produces samples from a non-central Chi-Squared random variable.

```{r}

c1 <- rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue")
c2 <- rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink")


plot(hist(NC_from_central_and_poisson(10,15,1000000), col = c1))
hist(rchisq(1000000, 15, ncp = 10), col = c2, add = TRUE)

```


Clearly, we can see that the function does generate a sample from the desired random variable. 
