normal_from_uni is a function that implements takes in three parameters: n, the desired amount of samples from a normal random variable, mu, the mean of the normal
random 
variable, and sd, the standard deviation of the random variable. 

The function checks to see if n is a non-negative integer and returns an error if it is not.

The function returns a vector of n observations that come from a normal random variable with mean mu and standard deviation sd. 

```{r}

normal_from_uni<- function(n,mu,sd){
  
  
if (n < 0 || n %% floor(n) != 0) {
stop("n must be a non-nagative integer")
}      
  
if ((n %% 2) == 0){
  
n_unifs <- runif(n,0,1)

rs <- sqrt(-2*log(1- n_unifs[1:(n/2)])) 
thetas <- 2*pi*n_unifs[(n/2+1):n]

y1s <- rs * cos(thetas)
y2s <- rs * sin(thetas)
}else{
n_unifs <- runif(n+1,0,1)

rs <- sqrt(-2*log(1- n_unifs[1:((n+1)/2)])) 
thetas <- 2*pi*n_unifs[((n+1)/2+1):(n+1)]

y1s <- rs * cos(thetas)
y2s <- rs[1:((n-1)/2)] * sin(thetas[1:((n-1)/2)])  
  
} 

  
ys <- c(y1s,y2s)

mu + ys*sd

}

```


Here, we verify that the function does generate samples from a normal(mu,sd^2) random variable by checking to see if the distribution lines up with the rnorm() 
function which we know produces samples from a normal(mu,sd^2) random variables.

```{r}

c1 <- rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue")
c2 <- rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink")


plot(hist(normal_from_uni(1000000, 10, 5), col = c1))
hist(rnorm(1000000,10,5), col = c2, add = TRUE)
```

Clearly, we can see that the function does generate a sample from the desired random variable. 

